Analyzing the impact of social attributes on commit integration success

### 2017-02-20 Paper/MSRChallenge2017.tex
todos through top of research design

\section{Introduction}
For managers of an open source project, it is important to ensure that the
project consists of high quality contributions.  The decision to include code in
a project has been described as a meritocracy, where only the code is a factor
in the decision~\cite{Scacchi07}.  Yet, as social coding sites continue to get
more users and specific projects become more popular, projects receive more
community contributions.  As the number of contributions to a project increase,
the project must dedicate more time to vetting these contributions.

Over the years, the open source
community has developed various techniques to vet project contributions, such as pull
requests which must be approved by a core team member~\cite{gousios14}. 
These methods can become a bottleneck, and to avoid a possible bottleneck, it is beneficial to prioritize certain
contributions.  This prioritization can be achieved with predictors of the
contribution's quality.

Past projects have shown that both technical factors, which describe the commit
and the project receiving the commit, and social factors, which describe the
developer making the commit, have been found useful when predicting a
contribution's quality~\cite{tsay14icse,tsay14fse}.
In this study we analyze a large set of technical and social attributes 
and how these can be used to predict a contributions quality, measured by the
success of build integration jobs.
We performed this analysis with a large corpus of open source projects
which incorporated continuous integration in their development practice. 
When a contribution to these projects pass integration tests, 
it shows that the project developers
have confidence in the changes. 
Thus, we can use the build integration status of the commit as documentation of
the commit's quality.

While past studies have analyzed pull request
success~\cite{tsay14icse,tsay14fse}, we are interested in analyzing the quality 
of a contribution in the context of continuous integration, we analyze the success every time a developer pushes a contribution to be built.
We analyzed contributions in the 
context of continuous integration, using the technical factors found in
some of the social attributes provided in the challenge
corpus~\cite{msr17challenge}, and the social factors found on a developer's
GitHub profile.  We used the technical factors to estimate the complexity of the
commit, and the social factors to estimate the developer's experience.

This study investigates how well different technical and social factors predict
contribution quality.  This information will help core team members prioritize project
contributions, and will also provide a further understand of quality enforcement
in the software development process.

\textbf{Related work:}
Similar studies have shown the relationship between different attributes and 
different measures of success: pull request acceptance~\cite{gousios14, 
gousios15,tsay14icse,tsay14fse}, pull request evaluation latency~\cite{Yu15}.
Tsay et al.~\cite{tsay14icse} performed a very relevant study where they 
determine that the social connection between the developer who is asking the 
pull request and the integrators is a key factor towards acceptance of a pull 
request. Unlike this previous study, in our study we look at a broader aspect of 
social aspects and how this attributes towards the success in Travis
CI jobs.\footnote{https://docs.travis-ci.com/user/customizing-the-build} 
Gousios et al.~\cite{gousios14} study the relationship between the area of the 
source code being modified by the developer requesting the changes to be pulled 
and the acceptance rate of these changes is highly correlated. Also existence of 
tests and overall code quality~\cite{gousios15} are attributes that have a 
strong relationship with the acceptance rate of a pull request. Bettenburgh et 
al.~\cite{bettenburgh10} discuss the impact of social interactions with 
post-release defects, Vasilescu et al.~\cite{vasilescu14} explored how different 
project characteristics (programming language, project age, etc.) affect commit 
success when integrated to the automatic build process. Yu et al.~\cite{yu16} 
analyze the impact of CI usage in GitHub and its correlation with software 
quality. Unlike the works previously listed, our study focuses on independent social 
attributes and how these relate to the success of the integration of a commit 
pushed by the developer being described by these social attributes.

Our study shows that social factors are an important aspect of build success but
these factors alone do not fully predict if a contribution will be successfully 
integrated into the project. We also show
that core team members are more likely to achieve build success than non-core
team members and a developer with followers is more likely to pass the
continuous integration build.

>>>>

\section{Introduction}
For managers of an open source project, it is important to ensure that the
project consists of high quality contributions.  As social coding sites attract
more users and projects become more popular, they receive ever more
community contributions.  As the number of contributions to a project increase,
the project must dedicate more time to vetting these contributions. 
%
Over the years, the open source
community has developed various techniques to vet project contributions, such as pull
requests which must be approved by a core team member~\cite{gousios14}. 
These methods can become a bottleneck, and thus it is beneficial to prioritize certain
contributions.  This prioritization can be achieved with predictors of a
contribution's quality.

The decision to include code in
a project has been described as a meritocracy, where only the code is a factor
in the decision~\cite{Scacchi07}.
However, past research 
has shown that both technical factors, which describe the commit
and the project receiving the commit, and social factors, which describe the
developer making the commit, have been found useful when predicting a
contribution's quality~\cite{tsay14icse,tsay14fse}.\todo{One or two more
  sentences, either here or earlier in the paragraph (between the first and
  second sentence), about why social factors might be interesting to study, or informative.}

This previous work has focused on the predicted acceptance of \emph{pull requests}. 
By contrast,  we are interested in analyzing the quality 
of a contribution in the context of continuous integration. \todo{What's the
  difference, and why might it matter? Why is CI interesting or different as
  compared to pull requests?(one sentence or so).} Thus, we propose to analyze the
success every time a developer pushes a contribution to be built. 
In this study, we analyze a large set of technical and social attributes 
and how these can be used to predict a contributions quality, measured by the
success of build integration jobs.
We performed this analysis on a large corpus of open source projects
which incorporated continuous integration in their development practice. 
When a contribution to these projects passes integration tests, 
it suggests that the project developers
might have confidence in the changes. 
Thus, we can use the build integration status of the commit as documentation of
the commit's quality.

In particular, we analyzed contributions in the 
context of continuous integration, using the technical factors found in
some\todo{First: don't use the word some basically ever.  Second: I'm not sure
  what it means to analyze technical factors found in social attributes.  Maybe rephrase?} of the social attributes provided in the challenge
corpus~\cite{msr17challenge}, and the social factors found on a developer's
GitHub profile.  We used the technical factors to estimate the complexity of the
commit, and the social factors to estimate the developer's experience.
Overall, our study investigates how well different technical and social factors predict
contribution quality.\todo{One sentence summary of results}  This information can help core team members prioritize project
contributions, and will also provide a further understand of quality enforcement
in the software development process.

\textbf{Related work:}
Similar studies have shown the relationship between different\todo{which?
  Social, technical?  Both?} attributes and 
different measures of success: pull request acceptance~\cite{gousios14, 
gousios15,tsay14icse,tsay14fse}, pull request evaluation latency~\cite{Yu15}.
Tsay et al.~\cite{tsay14icse} \todo{Read and delete this comment: one of you has
  a habit of saying something like ``...performed a very relevant study where
  they...'' in describing previous work.  This is needlessly wordy.  You can
  write the exact same sentence, more or less (I changed ``determine'' to
  ``show'', ``find'' might also work) without that clause} 
show that the social connection between the developer initiating a
pull request and the project integrators is a key factor towards acceptance of a pull 
\todo{I think you mean something like ``in predicting acceptance'', not
  ``towards''; do they argue causality?}
request. Unlike this previous study, in our study, we look at a broader aspect of 
social aspects and how this attributes\todo{wrong word (as in, this is a noun as
  used); I'm not sure what you mean so I can't fix it.}towards the success in Travis
CI jobs.\todo{Again, why are CI jobs interesting?  If you answre it appropriatey
  above you may not need to say it again here.} \footnote{https://docs.travis-ci.com/user/customizing-the-build} 
Gousios et al.~\cite{gousios14} study the relationship between the area of the 
source code being modified by the developer initiating a pull request 
and the acceptance rate of these changes is highly correlated.\todo{The
  preceding sentence is not grammatical.  Please fix.} Also existence of 
tests and overall code quality~\cite{gousios15} are attributes that have a 
strong relationship with the acceptance rate of a pull request.\todo{the
  previous sentence is not a sentence.} Bettenburgh et 
al.~\cite{bettenburgh10} discuss the impact of social interactions with 
post-release defects, Vasilescu et al.~\cite{vasilescu14} explore how different 
project characteristics (programming language, project age, etc.) affect commit 
success when integrated to\todo{wrong word} the automatic build process. Yu et al.~\cite{yu16} 
analyze the impact of CI usage in GitHub and its correlation with software 
quality. Unlike the works previously listed, we focus on independent social 
attributes and how these relate to the success of the integration of a commit 
pushed by the developer being described by these social attributes.

Our study shows that social factors are an important aspect of build success but
these factors alone do not fully predict if a contribution will be successfully 
integrated into the project. We also show
that core team members are more likely to achieve build success than non-core
team members and a developer with followers is more likely to pass the
continuous integration build.\todo{This paragraph doesn't really belong in the
  related work; I might move it above, near where I have a todo asking for a
  summary of results.}
